Validation challenges in large-scale tree crown segmentations from remote sensing imagery using Deep Learning: a case study in Germany

### 2025-06-11 Validation_challenges_tree_crown_segmentation/Draft1_PerspectivePaper.qmd
Update Draft1_PerspectivePaper.qmd
remove duplicate paragraph
Removed a duplicate paragraph on page 4.

---
title: "Validation challenges in large-scale tree crown segmentations from remote sensing imagery using Deep Learning: a case study in Germany"
title-running: Validation challenges in tree crown segmentations
bibliography: bibliography.bib
format:
  quarto-ecml-pdf:
    keep-tex: true
  quarto-ecml-html: default
author:
  - name: Taimur Khan
    orcid: '0000-0001-7833-5474'
    corresponding: true 
    affiliations:
      - name: Helmholtz Centre for Environmental Research (UFZ)
        address: Theodor-Lieser-Str. 4
        city: Halle (Saale)
        postal-code: 04109 
        country: Germany
        url: taimur.khan@ufz.de
        id: south
    url: https://www.ufz.de/index.php?en=49404
  - name: Jasmin Krebs
    orcid: '0009-0003-9330-1231'
    affiliations:
      - name: Leipzig University
        address: Augustusplatz 10 
        city: Leipzig
        country: Germany
        postal-code: 04109 
        url: jassi.krebs@gmx.de
  - name: Sharad Kumar Gupta
    orcid: '0000-1111-2222-3333'
    affiliations:
      - ref: south
      - name: Secondary European Affiliation
        address: Tiergartenstr. 17
        city: Heidelberg
        country: Germany
        postal-code: 69121 
        url: sharad.gupta@ufz.de
  - name: Jonathan Renkel
    orcid: '0000-1111-2222-3333'
    affiliations:
      - name: Martin Luther University Halle-Wittenberg
        address: Von-Seckendorff-Platz 2
        city: Halle (Saale)
        country: Germany
        postal-code: 06120
        url: jonathan.renkel@geo.uni-halle.de
  - name: Caroline Arnold
    orcid: '0000-0002-9458-1517'
    affiliations:
      - name: Helmholtz-Zentrum Hereon
        address: Max-Planck-Straße 1
        city: Geesthacht
        country: Germany
        postal-code: 21502 
        url: caroline.arnold@hereon.de
  - name: Nils Nölke 
    orcid: '0000-0003-4925-2287'
    affiliations:
      - name: University of Göttingen, Forest Inventory and Remote Sensing
        address: Büsgenweg 5
        city: Göttingen
        country: Germany
        postal-code: 37077 
        url: nils.noelke@forst.uni-goettingen.de

@@

Despite optimized methods, exact matches between predicted and ground-truth crown spreads were low (32%), though expanding the margin of error to ±5 m increased accuracy significantly (89%), highlighting validation challenges. The segmentation model systematically overestimated small crowns (\<6 m) and underestimated large crowns (\>16 m), yet the crown area versus spread relationship remained stable (Figure 1b), indicating consistent segmentations. Validation quality proved crucial; notably, the local inventory (‘Baumkataster’ Halle/Saale) provided broad intervals (5 m), limiting validation precision but still achieving an overall IOU of \~70%.The segmented tree crowns show substantial regional variability in tree distribution, reflecting ecological, topographical, and land-use gradients (Figure 3).

@@

# Appendices

@@

: Summary of key validation challenges in large-scale tree crown segmentation, with examples, relevant references, and recommended mitigation strategies. {#tbl-headings .tbl-colwidths="15,25,20,10,20,10"}

>>>>

---
title: "Validation challenges in large-scale tree crown segmentations from remote sensing imagery using Deep Learning: a case study in Germany"
title-running: Validation challenges in tree crown segmentations
bibliography: bibliography.bib
format:
  quarto-ecml-pdf:
    keep-tex: true
  quarto-ecml-html: default
author:
  - name: Taimur Khan
    orcid: '0000-0001-7833-5474'
    corresponding: true 
    affiliations:
      - name: Helmholtz Centre for Environmental Research (UFZ)
        address: Theodor-Lieser-Str. 4
        city: Halle (Saale)
        postal-code: 04109 
        country: Germany
        url: taimur.khan@ufz.de
        id: south
    url: https://www.ufz.de/index.php?en=49404
  - name: Jasmin Krebs
    orcid: '0009-0003-9330-1231'
    affiliations:
      - name: Leipzig University
        address: Augustusplatz 10 
        city: Leipzig
        country: Germany
        postal-code: 04109 
        url: jk21byxu@studserv.uni-leipzig.de
  - name: Sharad Kumar Gupta
    orcid: '0000-1111-2222-3333'
    affiliations:
      - ref: south
      - name: Secondary European Affiliation
        address: Tiergartenstr. 17
        city: Heidelberg
        country: Germany
        postal-code: 69121 
        url: sharad.gupta@ufz.de
  - name: Jonathan Renkel
    orcid: '0000-1111-2222-3333'
    affiliations:
      - name: Martin Luther University Halle-Wittenberg
        address: Von-Seckendorff-Platz 2
        city: Halle (Saale)
        country: Germany
        postal-code: 06120
        url: jonathan.renkel@geo.uni-halle.de
  - name: Caroline Arnold
    orcid: '0000-0002-9458-1517'
    affiliations:
      - name: Helmholtz-Zentrum Hereon
        address: Max-Planck-Straße 1
        city: Geesthacht
        country: Germany
        postal-code: 21502 
        url: caroline.arnold@hereon.de
  - name: Nils Nölke 
    orcid: '0000-0003-4925-2287'
    affiliations:
      - name: University of Göttingen, Forest Inventory and Remote Sensing
        address: Büsgenweg 5
        city: Göttingen
        country: Germany
        postal-code: 37077 
        url: nils.noelke@forst.uni-goettingen.de

@@

@@

<!--# Appendix

@@

: Summary of key validation challenges in large-scale tree crown segmentation, with examples, relevant references, and recommended mitigation strategies. {#tbl-headings .tbl-colwidths="15,25,20,10,20,10"}-->
